\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc} % переносы
% personal data
\firstname{Kharsky}
\familyname{Pavel}
\title{Curriculum Vitae}
\address{13 linia V.O.}{Apt 56 Saint Petersburg Russian Federation}
\mobile{+7~(931)~236~9243}
%\phone{+7~(927)~018~1021}
\email{kharskiy@gmail.com}
%\homepage{http://pashh.sytes.net} 
\extrainfo{https://github.com/pashh}
\extrainfo{Skype: uquark}
\begin{document}
\makecvtitle
\section{Education}
\cventry{2003--2008}{Samara State University}{Applied Physics}{Master of Science}{}{Laser applications; Optical vortices; Micromanipulation; Optics.}

\section{Employment}
\subsection{Vocational}
\cventry{2013--present time}{Senior Configuration manager}{T-Systems}{Saint Petersburg}{}{}
\cvline{}{Implementation and support continuous integration process for project }
\cvline{}{Prepare and deploy release version to customer}
\cvline{}{Improve project's configuration(upgrade process for Jboss from 5.2 to EAP 6.2 and interact with Red Hat support team)}
\cvline{}{Migrating a code history from ClearCase to git}
\cvline{}{}
%TODO

\cventry{2008--2013}{Release Engineer}{Netcracker}{Samara}{}{}
\cvline{}{Configuration Management} %Конфигурационное управление на проектах внедрения. 
\cvline{}{Optimizing, analysis and improve of workflow processes, workforce management.} %Оптимизация и поддержка процессов, на всех этапах, от сбора требований до саппортной активности.}
\cvline{}{Code review and merge, continuous integration, delivery practice.} %Ревью и мерж кода, подготовка и выдача релизного дропа заказчику.}
\cvline{}{Migrating from IBM Rational ClearCase - ant to SVN - Maven.} % Миграция проектов с IBM Rational ClearCase - ant на SVN - maven.}
\cvline{}{Teamwork with customer: Google, Sprint, Time Warner, France Telecom, Telus.}%  Работа в больших коммандах для заказчиков: Google, Sprint, Time Warner, France Telecom, Telus.}
\cvline{}{}

\cventry{2005--2008}{Engineer}{The Lebedev Physical Institute of the Russian Academy of Sciences (LPI RAS)}{Samara Branch}{}{} %Самарский Филиал Физического института им П.Н. Лебенева, Российской Академии Наук (РАН)}{Самара}{}{}
\cvline{}{Research and Development.}
\cvline{}{Empirical engineering.}
\cvline{}{Preparing a technical articles and scientific publications.}


\section{Language}
\cvitemwithcomment{Russian}{Native language.}{}
\cvitemwithcomment{English}{}{}
\section{Key skills}
\cvline{}{Python, Java, Ruby, Linux shell scripts.}

\cvline{Methodologies and practice:}{Object-oriented programming, Functional programming principles, Software design patterns, Software configuration management patterns, Agile, Waterfall, Kanban.}
\cvline{Version Control System:}{Git, Subversion, IBM Rational ClearCase.}
\cvline{Tools:}{JBoss, Weblogic, Unix(Slackware, Debian, FreeBSD), Apache/Nginx, Jenkins CI, Ant, Maven, Nexus repository, SonarQube, SoapUI, Emacs, MySql/Oracle, LaTex, Jira.}


\section{List of publications}
\cvitem{SPIE:}{One-dimensional and singular light fields: interconnection and analysis by means of astigmatic transform.  Proc. SPIE 6729, 67291C (2007); Digital Object Identifier: http://dx.doi.org/10.1117/12.752091}
\cvitem{Kazan. Gos. Univ. Uchen. Zap. Ser. Fiz.-Mat. Nauki 149:1}{Spiral beams analysis based on astigmatic transform (2007), 110–114}

\section{Awards}
\cvitem{}{Awards SPIE Educational Scholarship in Optical Science and Engineering 2007.}

%\clearpage

\section{Personal characteristics}
\cvline{}{High adaptability, excellent communication skills and managerial experience, high
teamwork capability, able to work hard, looking challenge, highly motivate and self-drive individual.}
\cvline{}{Determination, responsibility and absence of bad habits.}


% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    %\href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
