%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV for A4 paper format
% Based on XeLaTeX Template
%
% A4 version author:
% Marvin Frommhold (depressiverobot.com)
% https://github.com/depressiveRobot/friggeri-cv-a4
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
% example of compile: xelatex cv.tex
% for some strange reason you needs to compile this document twice! 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Options
% 'print': remove colors from this template for printing
% 'nocolors' to disable colors in section headers
\documentclass[nocolors]{friggeri-cv-a4}


\begin{document}

\header{Pavel}{Kharskiy}{DevOps Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
% SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Russian Federation,
Saint Petersburg,
13 linia V.O. Apt 56.
~
+7 (931) 236 9243
Skype: uquark
~
\href{mailto:kharskiy@gmail.com}{kharskiy@gmail.com}
\href{https://github.com/pashh}{https://github.com/pashh}
\section{languages}
russian mother tongue
english fluency
\section{programming}
Python, Java, Ruby, sql, pl/sql
Linux shell scripts
\section{vcs}
Git, Subversion, IBM Rational ClearCase
\section{tools}
JBoss, Weblogic, Unix(Linux, FreeBSD), Vagrant, Ansible, MySql/Oracle, Apache/Nginx, Jenkins CI, Ant, Maven, Gerrit, Nexus, SonarQube, SoapUI, Emacs, LaTex, Jira
\section{methodologies}
Object-oriented and
Functional programming principles,
Software design patterns,
Software configuration management patterns,
Agile, Waterfall, Kanban.
\end{aside}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------
  
\entry
{2003--2008}
{Masters { of Science}}
{Samara State University}
{\emph{Applied Physics} \\ Laser applications; Optical vortices; Micromanipulation; Optics.}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{T-Systems}
\begin{entrylist}
%------------------------------------------------
\entry
{2013--present time}
{Senior Configuration manager}
{Saint Petersburg}
{\emph{} \\
  Java application management.
  Implementation and support of automated/continuous build, deploy and test.
  Prepare release version for customer.
  Improve project's configuration(upgrade process for Jboss from 5.2 to EAP 6.2 and interact with Red Hat support team).
  Migrating a code history from ClearCase to git. \\
  %Contribute to the design and implementation of automated/continuous build, deploy, test and release process
  
}
%------------------------------------------------
\end{entrylist}

\subsection{Netcracker}
\begin{entrylist}
\entry
{2008--2013}
{Release Engineer}
{Samara}
{\emph{} \\
  Code review and merge, continuous integration, delivery practice.
  Migrating from IBM Rational ClearCase - ANT to SVN - Maven.
  Optimizing, analysing and improve of workflow processes, workforce management.
  Configuration Management.
  Teamwork with customers.  
}
\end{entrylist}


\subsection{The Lebedev Physical Institute of the Russian Academy of Sciences (LPI RAS)}
\begin{entrylist}
\entry
{2005--2008}
{Engineer}
{Samara}
{\emph{} \\
  Empirical engineering.
  Research and Development.
  Preparing a technical articles and scientific publications.
}

\end{entrylist}

%----------------------------------------------------------------------------------------
% AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}
\begin{entrylist}
\entry
{2007}
{SPIE}
{The international society for optics and photonics}
{Awards SPIE Educational Scholarship in Optical Science and Engineering.}
\end{entrylist}


%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\section{publications}
\begin{entrylist}
\entry
{2007}
{SPIE}
{Proc. SPIE 6729, 67291C (2007); Digital Object Identifier:
\href{http://dx.doi.org/10.1117/12.752091}{http://dx.doi.org/10.1117/12.752091}}
{One-dimensional and singular light fields: interconnection and analysis by means of astigmatic transform.}
\end{entrylist}

\begin{entrylist}
\entry
{2007}
{Kazan. Gos. Univ. Uchen. Zap.}
{Ser. Fiz.-Mat. Nauki 149:1 110–114}
{Spiral beams analysis based on astigmatic transform}
\end{entrylist}

\section{personal characteristics}
\textbf{}{High adaptability, high teamwork capability, able to work hard, excellent communication skills and managerial experience, looking challenge, highly motivate and self-drive individual.}
\textbf{}{Determination, responsibility and absence of bad habits.}

%----------------------------------------------------------------------------------------
% INTERESTS SECTION
%----------------------------------------------------------------------------------------
%\section{interests}
%\textbf{professional:}  web app creation, software design, marketing
%\textbf{personal:} piano, chess, cooking, dancing, running

%----------------------------------------------------------------------------------------

\end{document}
